\documentclass[]{sameer-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sameer}{Rathod}{ \urlstyle{same}\href{https://sameerportfolio.netlify.app/}{https://sameerportfolio.netlify.app/} \\
\href{mailto:sameerrathod1999@gmail.com}{sameerrathod1999@gmail.com} | \href{tel:9403137191}{+91-9403137191}|
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/in/sameerrathod1999}{\bf sameerRathod} \\
Github:// \href{https://github.com/Sameer411}{\bf Sameer411} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
        \subsection{K.K.W.I.E.E.R}
        \descript{B.E. - Computer Engineering}
        \location{2017 - 2021 | Nashik}
        \sectionsep
    
        \subsection{Bertelsmann \& Udacity}
        \descript{AI Product Manager}
        \location{2020 - 2021 | Virtual}
    \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Learnings 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Learnings} 
    \begin{itemize}
        \item Information Securities \\ in Big Data:  \href{https://sameerathod.wordpress.com/}{\bf Click to read} 

        \item New Era in Computer \\ Science: \href{https://sameerrathod99.wordpress.com/}{\bf Click to read} 
    \end{itemize}
    \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Java
    \item \textbf{Web Technologies:} HTML, CSS, Angular, React
    \item \textbf{Backend:} Java Spring Boot
    \item \textbf{Databases:} SQL
\end{itemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}
\begin{itemize}
    \item \textbf{English:} Professional Working
    \item \textbf{Hindi:} Professional Working
    \item \textbf{Gujarati:} Full Professional
    \item \textbf{Marathi:} Full Professional
\end{itemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACCOMPLISHMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Accomplishment}
\begin{itemize}
    \item \textbf{Most Valued Performer:} Great Learning - 2024
    \item \textbf{Top 7\% Coder:} Leetcode - 2023
\end{itemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{About Me}
With \textbf{4+ years of experience} in \textbf{software development}, I specialize in building \textbf{scalable, high-performance web applications} using \textbf{React, Angular, Spring Boot, and MySQL}. I have worked on \textbf{both front-end and back-end technologies}, ensuring seamless integration and optimal performance. Throughout my career, I have contributed to designing, developing, and deploying software solutions that enhance user experience and drive business growth.  
\vspace{1\baselineskip}
I am passionate about \textbf{continuous learning} and staying ahead of emerging technologies, which has enabled me to \textbf{lead and mentor development teams} effectively. My expertise in \textbf{software architecture, problem-solving, and performance optimization} allows me to create efficient, reliable, and maintainable solutions that align with business goals.

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{Sagility Health}
\descript{| Senior Technical Lead | Bangalore, IND}
\location{Nov 2024 - Present} 
\vspace{\topsep} 
\begin{tightemize}
\item Working as a \textbf{Software Developer \& Business Analyst}, contributing to product development and business strategy.
\item Developing a \textbf{Time \& Attendance platform} using \textbf{Java, Angular, and MySQL} to optimize workforce management.
\item \textbf{Gathering and analyzing} business requirements, converting them into \textbf{technical specifications} to ensure seamless alignment with \textbf{stakeholder needs}.
\item \textbf{Collaborating with cross-functional teams} (developers, testers, and business units) to enhance system usability and efficiency.
\item Implemented solutions that reduced financial leakage by \textbf{5-7\%}, improving overall cost efficiency.
\end{tightemize}
\sectionsep

\runsubsection{Great Learning}
\descript{| Software Engineer | Bangalore, IND}
\location{Dec 2022 – Nov 2024} 
\vspace{\topsep} 
\begin{tightemize}
\item \textbf{Versatile Full-Stack \& Product Developer} with expertise in \textbf{Java, Angular, and MySQL}, driving impactful solutions in EduTech.
\item \textbf{Developed a scalable Coding Lab Product} to enhance many users' learning and coding experience.
\item \textbf{Worked on both B2B and B2C business models}, ensuring seamless product adoption and customer engagement.
\item \textbf{Proficient in full-stack development}, including backend API design, frontend UI/UX enhancements, and database optimization.
\end{tightemize}
\sectionsep

\runsubsection{Google Cloud}
\descript{| Intern - Google Cloud Ready Facilitator | Nashik, IND}
\location{May 2021 – Jul 2021} 
\vspace{\topsep} 
\begin{tightemize}
\item Participated in the Google Cloud Ready Facilitator program.
\item Cloud Training \& Hands-on Labs - Worked on multiple Cloud labs on Qwiklabs.
\item Guided \textbf{almost 500 students} to successfully complete cloud labs and gain hands-on experience.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
